\documentclass[11pt,letterpaper]{article}
\newcommand{\workingDate}{\textsc{2023 $|$ April $|$ 12}}
\newcommand{\userName}{Xiangyu Zhou}
\newcommand{\institution}{Arizona State University}
\usepackage{graphicx} % Required for inserting images
\usepackage[colorlinks,linkcolor=blue]{hyperref}
\usepackage{listings}
\usepackage{float}
\usepackage{pythonhighlight}
\usepackage{researchdiary_png}

\begin{document}
\univlogo

\title{Reprot 2023.4.11}

{\Huge Report}

\section*{Previously scheduled Tasks}

\subsection*{1. ML Learning}

\subsection*{2. Power system Learning}

\subsection*{3. Derive the feasibility of fault classification}

\section*{Task Progress}

\subsection*{1. ML Learning}

Finished learning $Chapter\ 4: Artificial\ neural\ networks$ theoretically and completed the exercises at the end of the chapterand experimented with some outdated (unknown to me at first) python frameworks.

\subsection*{2. Power system Learning}

I had a meeting with Hamad yesterday, told him my understanding of the paper and determined the next tasks. In detail, we had a discussion on how to achieve the PI controller and how to determine the parameters of each simulation module.

\subsection*{3. Derive the feasibility of fault classification}

Not started yet.

\section*{Anything amazing}

I really didn't think of anything amazing this week.

\section*{The next tasks}

\subsection*{1. Do experiments on face recognition}

In $chapter\ 4$, there is an example of face recognition written in C language. I decide to run it first and search if there is another way to achieve face recognition such as pytorch.

\subsection*{2. Finish the simulation}

I plan to complete the design of the simulation block diagram within three days and adjust the parameters in the following two weeks.

\subsection*{3. Finishing derive the feasibility of fault classification}

I'm not sure if there is enough time for me to finish it this week and it is not urgent after all, but I'm sure it will be done this month.

\end{document}
